Quality Assesment of OpenStreetMap Footpath Data

### 2020-06-11 report/report.tex
Update remaning Implementation chapter

For the purpose of this project, the OSM road dataset has been sampled around Stockholm metropolitan area.
To assess and correct path widths and path node locations, the OSM building footprint dataset areound the same area has also been used.
As a reference dataset, the property map from the Swedish National Land Survey was used in comparison with the OSM map.
The reference map is provided by the Swedish University of Agricultural Sciences (SLU), and will be referred to in this report as the SLU map or the SLU dataset.
The SLU map conatins only building and property footprints.
The exact map segments that were extracted were in both cases rectangular boundaries with the following coordinates in WGS84: (N: 59.42, E: 18.15, S: 59.23, W: 17.79).
Both datasets were collcted on March 18th, 2020.

@@

The SLU map is maintained by The Swedish National Land Survey (Swedish: Lantmäteriet)
\footnote{Lantmäteriet. Produktbeskrivning: GSD-Fastighetskartan vektor - Lantmäteriet. Acessed 16-04-2020. https://www.lantmateriet.se/globalassets/kartor-och-geografisk-information/kartor/fastshmi.pdf}.
The data is collected by geodetic professionals, by land surveying methods such as GPS or DGNSS positioning, or by reproduction of features from ortophoto or stereo mapping from 3D aerial images.
Building features in the SLU dataset have a position accuracy requirement of 2 meters.
The SLU map contains building features and property limits, but no road data.
The map is updated continously by Lantmäteriet, in conjoncture with the forming or reforming of property.
Whereas OSM is a free service, the SLU map is available to paying customers or for free to students and researchers.

>>>>

This project used a slice of the OSM road and building datasets around the Stockholm metropolitan area.
As a reference dataset, the property map from the Swedish National Land Survey was used in comparison with the OSM map.
The reference map is provided by the Swedish University of Agricultural Sciences (SLU), and will be referred to in this report as the SLU map or the SLU dataset.
The SLU map conatins only building and property footprints.
The exact map segments that were extracted were in both cases rectangular boundaries with the following coordinates in WGS84: (N: 59.42, E: 18.15, S: 59.23, W: 17.79).
Both datasets were collcted on March 18th, 2020.

@@

The SLU map is maintained by The Swedish National Land Survey (Swedish: Lantmäteriet)
\footnote{Lantmäteriet. Produktbeskrivning: GSD-Fastighetskartan vektor - Lantmäteriet. Acessed 16-04-2020. https://www.lantmateriet.se/globalassets/kartor-och-geografisk-information/kartor/fastshmi.pdf}.
The data is collected by geodetic professionals, by using land surveying methods such as GPS or DGNSS positioning, or by reproduction of features from ortophoto or stereo mapping from 3D aerial images.
Building features in the SLU dataset have a position accuracy requirement of 2 meters.
The SLU map contains building features and property limits, but no road data.
The map is updated continously by Lantmäteriet, in conjoncture with the forming or reforming of property.
Whereas OSM is a free service, the SLU map is available to paying customers or for free to students and researchers.
